Laplacian envelope

### 2020-07-15 Notes/laplace.tex
interpretation of laplace FPT

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
% arXiv Paper ************************************************
%
% Subhaneil Lahiri's template
%
% Before submitting:
%    Comment out hyperref
%    Comment out showkeys
%    Replace \input{?.tex} with its contents
%       or include ?.tex in zip/tar file
%    Put this file, the .bbl file, any picture or
%       other additional files and natbib.sty
%       file in a zip/tar file
%
% **** -----------------------------------------------------------
\documentclass[12pt]{article}
%Preamble:
\usepackage{a4wide}
\input{sl_preamble.tex}
\usepackage{mathtools}
%
% >> Only for drafts! <<
\usepackage[notref,notcite]{showkeys}
%
\input{sl_graphics_preamble.tex}
\graphicspath{{Figures/}}
%
% ----------------------------------------------------------------
%\numberwithin{equation}{section}
%\renewcommand{\baselinestretch}{1.5}
% ----------------------------------------------------------------
% New commands etc.
\input{sl_definitions.tex}
\input{sl_symbols.tex}
%matrices
%vec of ones
\newcommand{\onev}{\mathbf{e}}
%mat of ones
\newcommand{\onem}{\mathbf{E}}
%Markov matrix
\newcommand{\MM}{\mathbf{Q}}
%prob distribution
\newcommand{\pr}{\mathbf{p}}
%equilibrium distribution
\newcommand{\eq}{\pr^\infty}
%first passage times
\newcommand{\fpt}{\mathbf{T}}
%off-diag first passage times
\newcommand{\fptb}{\overline{\fpt}}
%fundamental matrix
\newcommand{\fund}{\mathbf{Z}}
%other symbols
\newcommand{\Pb}{\mathbf{P}}
\newcommand{\D}{\mathbf{D}}
\newcommand{\pib}{\boldsymbol{\pi}}
\newcommand{\arow}{\boldsymbol{\xi}}
\newcommand{\Lb}{\boldsymbol{\Lambda}}
\newcommand{\etw}{\boldsymbol{\eta}^w}
\newcommand{\thb}{\boldsymbol{\theta}}
%synapse models
\newcommand{\w}{\mathbf{w}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\enc}{\mathbf{K}}
\newcommand{\frg}{\W^{\mathrm{F}}}
\newcommand{\F}{\boldsymbol{\Phi}}
%superscripts
\newcommand{\pot}{^{\text{pot}}}
\newcommand{\dep}{^{\text{dep}}}
\newcommand{\potdep}{^{\text{pot/dep}}}
%with activity indep processes
\renewcommand{\hom}{\mathbf{H}}
\newcommand{\Mh}{\widetilde{\M}}
\newcommand{\frgh}{\widetilde{\W}^{\mathrm{F}}}
\newcommand{\ench}{\widetilde{\enc}}
%eigenvectors
\newcommand{\evr}{\mathbf{u}}
\newcommand{\evl}{\boldsymbol{\eta}}
%snr curves etc
\newcommand{\syn}{\vec{w}}
\newcommand{\synid}{\syn_\text{id}}
\DeclareMathOperator{\SNR}{SNR}
\DeclareMathOperator{\snr}{SNR}
\DeclareMathOperator{\NNR}{NNR}
\DeclareMathOperator{\nnr}{NNR}
\newcommand{\snrb}{\overline{\snr}}
\DeclareMathOperator{\env}{Env}
\newcommand{\rh}{\hat{r}}
\newcommand{\CA}{\mathcal{A}}
\newcommand{\CB}{\mathcal{B}}
%avoid double superscripts
\renewcommand{\pdiff}[2]{\frac{\partial #1}{\partial #2}}

@@

Then we also define
%
\begin{equation}\label{eq:lfptb}
  \fptb(s) = (\onem \fund\dg(s)-\fund(s))\D,
  \qquad
  \fptb_{ij}(s) = \frac{\fund_{jj}(s)-\fund_{ij}(s)}{\eq_j}.
\end{equation}
%
This reduces to the first passage time matrix at $s=0$, but at other $s$ there is (probably) no relation.

Using the exact same proof as in the case $s=0$, we see that the quantity
%
\begin{equation}\label{eq:lkemeny}
  \eta(s) = \sum_j \fptb_{ij}(s)\eq_j
\end{equation}
%
is independent of the starting state $i$, but now $\eta(s) = \tr\fund(s) - \frac{\tau}{1+s\tau}$.
We can then define
%
\begin{equation}\label{eq:lpmixtime}
  \eta^{\pm}_i(s) = \sum_j \fptb_{ij}(s) \eq_j \prn{\frac{1 \pm \w_j}{2}} 
      =  \sum_{j\in \pm} \fptb_{ij}(s) \eq_j.
\end{equation}
%
We can arrange the states in order of decreasing $\eta^{+}_i(s)$ or increasing $\eta^{-}_i(s)$.
It will be more convenient to use the quantities
%
\begin{equation}\label{eq:lwpmixtime}
  \etw_i(s) = \sum_j \fptb_{ij}(s)\eq_j \w_j
    = \eta^+_i(s) - \eta^-_i(s) 
    = 2\eta^+_i(s) - \eta(s) 
    = \eta(s) - 2\eta^-_i(s) .
\end{equation}
%
Arranging the states in order of decreasing $\etw_i(s)$ is the same as the order of decreasing $\eta^{+}_i(s)$ or increasing $\eta^{-}_i(s)$.
The $\etw_i(s)$ can still be used when $\w$ takes more than two values.

@@

Now consider the Laplace transform of the SNR curve \eqref{eq:SNRcurveExact}
%
\begin{equation}\label{eq:lsnr}
\begin{aligned}
  A(s) = \intd[_0^{\infty}]{t} \e^{-st}\SNR(t) 
   &= \intd[_0^{\infty}]{t} \frac{ \sqrt{N} \eq \enc \e^{(r\frg-s)t} \w }
                                { \sqrt{1-(f\pot-f\dep)^2(\eq\w)^2} } \\
   &= \frac{\sqrt{N} \eq \enc \prn{s - r\frg}\inv \w }{\sqrt{1-(f\pot-f\dep)^2(\eq\w)^2}}.
\end{aligned}
\end{equation}
%
This expression is ill-behaved at $s=0$.
Thanks to \eqref{eq:alfund}, we can solve this by the replacement $\mathbf{G}(s) \to \fund(s)$, as $\enc\onev=0$.
%
\begin{equation}\label{eq:larea}
\begin{aligned}
  \hat{A}(s) = A(s) \sqrt{\frac{{{1-(f\pot-f\dep)^2(\eq\w)^2}}}{N}}  &=  \eq \enc \fund(s) \w \\
    &= \sum_{ijk} \eq_i \enc_{ij} \prn{\fptb_{ik}(s)-\fptb_{jk}(s)} \eq_k \w_k \\
    &= \sum_{ij}  \eq_i \enc_{ij} (\etw_{i}(s) - \etw_{j}(s)).
\end{aligned}
\end{equation}
%
Note that $A(0)=A$, the area, and $\lim_{s\to\infty} \brc{sA(s)} = \SNR(0)$, the initial SNR.

In analogy with the case $s=0$, we define
%
\begin{equation}\label{eq:lareacoeffs}
  \begin{aligned}
    c_k(s) &= \sum_{ij} \eq_i \enc_{ij} \prn{\fptb_{ik}(s)-\fptb_{jk}(s)}, \\
    a_j(s) &= \sum_{k} \enc_{jk} (\etw_{j}(s) - \etw_{k}(s)), \\
    \thb_i(s) &= \sum_j \fptb_{ij}(0)\, \eq_j a_j(s), \\
  \end{aligned}
    \implies
    \hat{A}(s) = \sum_k c_k(s) \eq_k \w_k
      = \sum_i  \eq_i a_i(s).
\end{equation}
%

@@

Using the same approach as the area bound in \cite{Lahiri2013synapse} we find that the derivatives are
%
\begin{equation}\label{eq:lAdiff}
  \pdiff{\hat{A}(s)}{\M^\mu_{mn}}
     = f^\mu \eq_m \prn{ r \brk{\thb_m(s) - \thb_n(s)}
     +\prn{rc_m(s) + (-1)^\mu} \brk{\etw_m(s) - \etw_n(s)} }.
\end{equation}
%
The term with $\Theta(s)$ comes from differentiating $\eq$, the term with $c(s)$ comes from differentiating $\etw(s)$ and the term with $\pm1$ comes from differentiating $\enc$ in \eqref{eq:larea}.

To write down the Hessian, we will first define some notation.
We define the matrix $\mathbf{X}(s) = \fund(0) \enc \fund(s)$.
Given a four-index array $H_{ijkl}$, we define $H\trans_{ijkl} = H_{klij}$.
Then we denote
%
\begin{equation}\label{eq:hessparts}
\begin{alignedat}{3}
    R_{ijkl} &= \
    &&\eq_i \brc{\fund_{ik}(0) - \fund_{jk}(0)} \brc{\thb_k(s) - \thb_l(s)} \\
    &&&+ \eq_i \brc{\mathbf{X}_{ik}(s) - \mathbf{X}_{jk}(s)} 
          \brc{\etw_k(s) - \etw_l(s)} \\
    &&&+ \eq_i c_i(s) \brc{\fund_{ik}(s) - \fund_{jk}(s)} 
          \brc{\etw_k(s) - \etw_l(s)},  \\
  S_{ijkl} &=
    &&\eq_i \brc{\fund_{ik}(0) - \fund_{jk}(0)} \brc{\etw_k(s) - \etw_l(s)} \\
    &&&+ \eq_k \brc{\fund_{ki}(s) - \fund_{li}(s)} \brc{\etw_i(s) - \etw_j(s)}.
\end{alignedat}
\end{equation}
%
Then we can write the Hessian as
%
\begin{equation}\label{eq:hessian}
  \pdiff{^2\hat{A}(s)}{\M^\mu_{ij} \partial\M^\nu_{kl}} =
     f^\mu f^\nu [R + R\trans + (-1)^\nu S + (-1)^\mu S\trans]_{ijkl}.
\end{equation}
%
This is useful in numerical maximisation.

@@

Now we'll maximise $\snrb(\tau)$ for some fixed $\tau$, subject to the constraints \eqref{eq:constr}.
First, we will maximise the numerator of \eqref{eq:lsnr} holding $\eq\w$ fixed.
We can maximise the ration \wrt $\eq\w$ later.
Consider the Lagrangian
%
\begin{equation}\label{eq:finitelagrangian}
\begin{aligned}
  \CL =&\, \sum_{ij} \eq_i \enc_{ij} (\etw_i(s) - \etw_j(s))
        +\sum_{\nu i j} \prn{ f^\nu \mu^\nu_{ij} \M\pot_{ij} }
        &+ \lambda \prn{ \Delta\pr - \sum_i \eq_i\w_i },
\end{aligned}
\end{equation}
%
where $\Delta\pr$ is the constant value we are holding $\eq\w$ at.
After maximising
The Karush-Kuhn-Tucker necessary conditions for a maximum are
%
\begin{equation}\label{eq:KTfinite}
  \pdiff{\CL}{\M^\nu_{ij}} = 0, \quad
  \mu^\nu_{ij} \geq 0, \quad
  \pdiff{\CL}{\mu^\nu_{ij}} \geq 0, \quad
  \mu^\nu_{ij}\pdiff{\CL}{\mu^\nu_{ij}} = 0, \quad
  \pdiff{\CL}{\lambda} = 0.
\end{equation}
%
The derivatives, for $m \neq n$ are
%
\begin{equation}\label{eq:finitederivs}
\begin{aligned}
  \frac{1}{f^\nu} \pdiff{\CL}{\Mh^\nu_{mn}} = & \,
      \eq_m \prn{ r \brk{\thb_m(s) - \thb_n(s)}
     +\prn{rc_m(s) + (-1)^\nu} \brk{\etw_m(s) - \etw_n(s)} } \\
     &+ \mu^\nu_{mn} -  \mu^\nu_{mm}
     + \lambda \eq_m \sum_i (\fptb_{mi}(0)-\fptb_{ni}(0)) \eq_i\w_i.
\end{aligned}
\end{equation}
%
These have the same form as for $s=0$, which allowed us to argue that the model with maximal area must have the serial topology, \cite{Leibold2008serial,Ben-DayanRubin2007sparse}.

The one missing ingredient is the scale invariance.
Define the scale transformation:
%
\begin{equation}\label{eq:scale}
  \lambda * \M = (1-\lambda)\I + \lambda \M.
\end{equation}
%
The Laplace transform has the following scaling property
%
\begin{equation}\label{eqlaplacescale}
  A(\lambda s;\lambda * \M^\nu) = A(s;\M^\nu).
\end{equation}
%
At $s=0$, it is scale invariant.
This means that we can take a pair of matrices that violates the ``diagonal'' constraints (second inequality of \eqref{eq:constri}) and use the scale transform \eqref{eq:scale} to construct a pair of matrices that satisfy the ``diagonal'' constraints and have the same area.
This allowed us to ignore the diagonal constraints.
We can't do that for $s>0$.

@@

>>>>

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
% arXiv Paper ************************************************
%
% Subhaneil Lahiri's template
%
% Before submitting:
%    Comment out hyperref
%    Comment out showkeys
%    Replace \input{?.tex} with its contents
%       or include ?.tex in zip/tar file
%    Put this file, the .bbl file, any picture or
%       other additional files and natbib.sty
%       file in a zip/tar file
%
% **** -----------------------------------------------------------
\documentclass[12pt]{article}
%Preamble:
\usepackage{a4wide}
\input{sl_preamble.tex}
\usepackage{mathtools}
%
% >> Only for drafts! <<
\usepackage[notref,notcite]{showkeys}
%
\input{sl_graphics_preamble.tex}
\graphicspath{{Figures/}}
%
% ----------------------------------------------------------------
%\numberwithin{equation}{section}
%\renewcommand{\baselinestretch}{1.5}
% ----------------------------------------------------------------
% New commands etc.
\input{sl_definitions.tex}
\input{sl_symbols.tex}
%matrices
%vec of ones
\newcommand{\onev}{\mathbf{e}}
%mat of ones
\newcommand{\onem}{\mathbf{E}}
%Markov matrix
\newcommand{\MM}{\mathbf{Q}}
%prob distribution
\newcommand{\pr}{\mathbf{p}}
%equilibrium distribution
\newcommand{\eq}{\pib}
%equilibrium metric
\newcommand{\Eq}{\boldsymbol{\Pi}}
%first passage times
\newcommand{\fpt}{\mathbf{T}}
%off-diag first passage times
\newcommand{\fptb}{\overline{\fpt}}
%fundamental matrix
\newcommand{\fund}{\mathbf{Z}}
%other symbols
\newcommand{\Pb}{\mathbf{P}}
\newcommand{\D}{\mathbf{D}}
\newcommand{\pib}{\boldsymbol{\pi}}
\newcommand{\arow}{\boldsymbol{\xi}}
\newcommand{\Lb}{\boldsymbol{\Lambda}}
\newcommand{\etw}{\boldsymbol{\eta}^w}
\newcommand{\thb}{\boldsymbol{\theta}}
\newcommand{\omb}{\boldsymbol{\omega}}
\newcommand{\alb}{\boldsymbol{\alpha}}
%synapse models
\newcommand{\w}{\mathbf{w}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\enc}{\mathbf{K}}
\newcommand{\frg}{\W^{\mathrm{F}}}
\newcommand{\F}{\boldsymbol{\Phi}}
%superscripts
\newcommand{\pot}{^{\text{pot}}}
\newcommand{\dep}{^{\text{dep}}}
\newcommand{\potdep}{^{\text{pot/dep}}}
%with activity indep processes
\renewcommand{\hom}{\mathbf{H}}
\newcommand{\Mh}{\widetilde{\M}}
\newcommand{\frgh}{\widetilde{\W}^{\mathrm{F}}}
\newcommand{\ench}{\widetilde{\enc}}
%eigenvectors
\newcommand{\evr}{\mathbf{u}}
\newcommand{\evl}{\boldsymbol{\eta}}
%snr curves etc
\newcommand{\syn}{\vec{w}}
\newcommand{\synid}{\syn_\text{id}}
\DeclareMathOperator{\SNR}{SNR}
\DeclareMathOperator{\snr}{SNR}
\DeclareMathOperator{\NNR}{NNR}
\DeclareMathOperator{\nnr}{NNR}
\newcommand{\snrb}{\overline{\snr}}
\DeclareMathOperator{\env}{Env}
\newcommand{\rh}{\hat{r}}
\newcommand{\CA}{\mathcal{A}}
\newcommand{\CB}{\mathcal{B}}
%avoid double superscripts
\renewcommand{\pdiff}[2]{\frac{\partial #1}{\partial #2}}
% shifted process
\newcommand{\shift}[1]{\widehat{#1}}

@@

Then we also define
%
\begin{equation}\label{eq:lfptb}
  \fptb(s) = (\onem \fund\dg(s)-\fund(s))\D,
  \qquad
  \fptb_{ij}(s) = \frac{\fund_{jj}(s)-\fund_{ij}(s)}{\eq_j}.
\end{equation}
%
This reduces to the mean first-passage time matrix at $s=0$.

At other values of \(s\) can they be interpreted as the mean first-passage times of a different process?
In order to have \cref{eq:lfund} as its fundamental matrix, the extra bit must draw probability from each state at a rate \(s\).
In other words, it should have the form \(s(\onev \boldsymbol{\zeta} - \I)\) for some \(\boldsymbol{\zeta} \) 
(which can be absorbed into \(\arow\) in \cref{eq:lfund}).
This other process must have the same steady-state distribution, so that its mean first-passage times are given by \cref{eq:lfptb}, so the probability drawn from each state must be redistributed proportional to \(\eq\).
This other stochastic process is
%
\begin{equation}\label{eq:lshift}
  \shift{\MM}(s) = \MM + s (\onev \eq - \I).
\end{equation}
%
This is a valid continuous-time Markov process.
Its fundamental matrix is given by \cref{eq:lfund} with \( \arow_0 = \arow + s \eq \).

This means that the \( \fptb(s) \) have all the same properties as in the case $s=0$.
I particular, we see that the quantity
%
\begin{equation}\label{eq:lkemeny}
  \eta(s) = \sum_j \fptb_{ij}(s)\eq_j
\end{equation}
%
is independent of the starting state $i$, but now $\eta(s) = \tr\fund(s) - \frac{\tau_0}{1 + s \tau_0}$.
We can then define
%
\begin{equation}\label{eq:lpmixtime}
  \eta^{\pm}_i(s) = \sum_j \fptb_{ij}(s) \eq_j \prn{\frac{1 \pm \w_j}{2}} 
      =  \sum_{j\in \pm} \fptb_{ij}(s) \eq_j.
\end{equation}
%
We can arrange the states in order of decreasing $\eta^{+}_i(s)$ or increasing $\eta^{-}_i(s)$.
It will be more convenient to use the quantities
%
\begin{equation}\label{eq:lwpmixtime}
  \etw_i(s) = \sum_j \fptb_{ij}(s)\eq_j \w_j
    = \eta^+_i(s) - \eta^-_i(s) 
    = 2\eta^+_i(s) - \eta(s) 
    = \eta(s) - 2\eta^-_i(s) .
\end{equation}
%
Arranging the states in order of decreasing $\etw_i(s)$ is the same as the order of decreasing $\eta^{+}_i(s)$ or increasing $\eta^{-}_i(s)$.
The $\etw_i(s)$ can still be used when $\w$ takes more than two values.

@@

Now consider the Laplace transform of the SNR curve \eqref{eq:SNRcurveExact}
%
\begin{equation}\label{eq:lsnr}
\begin{aligned}
  A(s) = \intd[_0^{\infty}]{t} \e^{-st}\SNR(t) 
   &= \intd[_0^{\infty}]{t} \frac{ \sqrt{N} \eq \enc \e^{(r\frg-s)t} \w }
                                { \sqrt{1-(f\pot-f\dep)^2(\eq\w)^2} } \\
   &= \frac{\sqrt{N} \eq \enc \prn{s \I - r\frg}\inv \w }{\sqrt{1-(f\pot-f\dep)^2(\eq\w)^2}}.
\end{aligned}
\end{equation}
%
This expression is ill-behaved at $s=0$.
Thanks to \eqref{eq:alfund}, we can solve this by the replacement $\mathbf{G}(s) \to \fund(s)$, as $\enc\onev=0$.
%
\begin{equation}\label{eq:larea}
\begin{aligned}
  \hat{A}(s) = A(s) \sqrt{\frac{{{1-(f\pot-f\dep)^2(\eq\w)^2}}}{N}}  &=  \eq \enc \fund(s) \w \\
    &= \sum_{ijk} \eq_i \enc_{ij} \prn{\fptb_{ik}(s)-\fptb_{jk}(s)} \eq_k \w_k \\
    &= \sum_{ij}  \eq_i \enc_{ij} (\etw_{i}(s) - \etw_{j}(s)).
\end{aligned}
\end{equation}
%
Note that $A(0)=A$, the area, and $\lim_{s\to\infty} \brc{sA(s)} = \SNR(0)$, the initial SNR.

We can also express this in terms of the shifted process in \cref{eq:larea}.
We can choose how to distribute the shift across \(\M\pot\) and \(\M\dep\).
Two choices from a continuum%
\footnote{We could choose \( \shift{\M}^\nu(s) = \M^\nu + \frac{s g^\nu}{r f^\nu} (\onev \eq - \I) \), for any \(g^\nu \) with \( \sum_\nu g^\nu = 1 \).
The two possibilities in \cref{eq:lshiftpd} come from \(g^\nu = \frac{1}{2}\) and \(g^\nu = f^\nu\) respectively.}
are:
%
\begin{equation}\label{eq:lshiftpd}
  \shift{\M}^\nu(s) = \M^\nu + \frac{s}{2 r f^\nu} (\onev \eq - \I)
  \qquad \text{or} \qquad
  \shift{\M}^\nu(s) = \M^\nu + \frac{s}{r} (\onev \eq - \I).
\end{equation}
%
The first choice leaves \( \shift{\enc} = \enc \), so it only affects the \(\etw\) piece of \cref{eq:larea}.
The second choice does not leave \(\enc\) invariant (in fact \( \shift{\enc}(s) = \enc + (f\pot - d\dep) (\onev \eq - \I) \)), but because \( \eq (\onev \eq - \I) = 0 \) the shift does not make any contribution to \cref{eq:larea}.
Either way:
%
\begin{equation}\label{eq:lareashift}
  \hat{A}\prn{s; \M^\nu} = \hat{A}\prn{0; \shift{\M}^\nu(s)}.
\end{equation}
%
In other words, the laplace transform of the SNR is the area under the SNR for the shifted process.

Note that while \cref{eq:lshift} produces a valid continuous-time Markov process, \cref{eq:lshiftpd} does not always produce valid discrete-time Markov processes, as the diagonal elements can become negative.
However, \(r (\shift{\M}^\nu - \I)\) is a valid continuous-time Markov process.

In analogy with the case $s=0$, we define
%
\begin{equation}\label{eq:lareacoeffs}
  \begin{aligned}
    \mathbf{c}_k(s) &= \sum_{ij} \eq_i \enc_{ij} \prn{\fptb_{ik}(s)-\fptb_{jk}(s)}, \\
    \mathbf{a}_j(s) &= \sum_{k} \enc_{jk} (\etw_{j}(s) - \etw_{k}(s)), \\
    \thb_i(s) &= \sum_j \fptb_{ij}(0)\, \eq_j \mathbf{a}_j(s), \\
  \end{aligned}
    \implies
    \hat{A}(s) 
      = \sum_k \eq_k \mathbf{c}_k(s) \w_k
      % = \mathbf{c}^\dag(s) \w
      = \eq \mathbf{a}(s).
\end{equation}
%

@@

Using the same approach as the area bound in \cite{Lahiri2013synapse} we find that the derivatives are
%
\begin{equation}\label{eq:lAdiff}
  \pdiff{\hat{A}(s)}{\M^\mu_{mn}}
     = f^\mu \eq_m \prn{ r \brk{\thb_m(s) - \thb_n(s)}
     +\prn{r \mathbf{c}_m(s) + (-1)^\mu} \brk{\etw_m(s) - \etw_n(s)} }.
\end{equation}
%
The term with $\Theta(s)$ comes from differentiating $\eq$, the term with $c(s)$ comes from differentiating $\etw(s)$ and the term with $\pm1$ comes from differentiating $\enc$ in \eqref{eq:larea}.

To write down the Hessian, we will first define some notation.
We define the matrix $\mathbf{X}(s) = \fund(0) \enc \fund(s)$.
Given a four-index array $H_{ijkl}$, we define $H\trans_{ijkl} = H_{klij}$.
Then we denote
%
\begin{equation}\label{eq:hessparts}
\begin{alignedat}{3}
    R_{ijkl} = \smash{\pdiff{^2 \hat{A}}{\frg_{ij} \circ \partial \frg_{kl}}} 
    &= \
    &&\eq_i \brc{\fund_{ik}(0) - \fund_{jk}(0)} \brc{\thb_k(s) - \thb_l(s)} \\
    &&&+ \eq_i \brc{\mathbf{X}_{ik}(s) - \mathbf{X}_{jk}(s)} 
          \brc{\etw_k(s) - \etw_l(s)} \\
    &&&+ \eq_i \mathbf{c}_i(s) \brc{\fund_{ik}(s) - \fund_{jk}(s)} 
          \brc{\etw_k(s) - \etw_l(s)},  \\
  S_{ijkl} = \smash{\pdiff{^2 \hat{A}}{\frg_{ij} \partial \enc_{kl}} }
  &= \
    &&\eq_i \brc{\fund_{ik}(0) - \fund_{jk}(0)} \brc{\etw_k(s) - \etw_l(s)} \\
    &&&+ \eq_k \brc{\fund_{ki}(s) - \fund_{li}(s)} \brc{\etw_i(s) - \etw_j(s)},
\end{alignedat}
\end{equation}
%
where \(R\) contains only those terms where \( \frg_{ij} \) precedes \( \frg_{kl} \) in the matrix products from the expression for \( \hat{A} \) in \cref{eq:larea}.
The other terms sum to \(R\trans\).

Then we can write the Hessian as
%
\begin{equation}\label{eq:hessian}
  \pdiff{^2\hat{A}(s)}{\M^\mu_{ij} \partial\M^\nu_{kl}} =
     f^\mu f^\nu [R + R\trans + (-1)^\mu S\trans + (-1)^\nu S]_{ijkl}.
\end{equation}
%
This is useful in numerical maximisation.

@@

Now we'll maximise $\snrb(\tau)$ for some fixed $\tau$, subject to the constraints \eqref{eq:constr}.
First, we will maximise the numerator of \eqref{eq:lsnr} holding $\eq\w$ fixed.
We can maximise the ration \wrt $\eq\w$ later.
Consider the Lagrangian
%
\begin{equation}\label{eq:finitelagrangian}
\begin{aligned}
  \CL =&\, \sum_{ij} \eq_i \enc_{ij} (\etw_i(s) - \etw_j(s))
        +\sum_{\nu i j} \prn{ f^\nu \mu^\nu_{ij} \M^\nu_{ij} }
        &+ \lambda \prn{ \Delta\pr - \sum_i \eq_i\w_i },
\end{aligned}
\end{equation}
%
where $\Delta\pr$ is the constant value we are holding $\eq\w$ at.
The Karush-Kuhn-Tucker necessary conditions for a maximum are
%
\begin{equation}\label{eq:KTfinite}
  \pdiff{\CL}{\M^\nu_{ij}} = 0, \quad
  \mu^\nu_{ij} \geq 0, \quad
  \pdiff{\CL}{\mu^\nu_{ij}} \geq 0, \quad
  \mu^\nu_{ij}\pdiff{\CL}{\mu^\nu_{ij}} = 0, \quad
  \pdiff{\CL}{\lambda} = 0.
\end{equation}
%
We have scaled the KKT multipliers by \(f^\nu\) for later convenience.

The derivatives, for $m \neq n$ are
%
\begin{equation}\label{eq:finitederivs}
\begin{aligned}
  \frac{1}{f^\nu} \pdiff{\CL}{\Mh^\nu_{mn}} = & \,
    \eq_m \prn{ r \brk{\thb_m(s) - \thb_n(s)}
     + \prn{r \mathbf{c}_m(s) + (-1)^\nu} \brk{\etw_m(s) - \etw_n(s)} } \\
     &+ \mu^\nu_{mn} -  \mu^\nu_{mm}
     + r \lambda \eq_m (\etw_{m}(0)-\etw_{n}(0)) 
    = 0.
\end{aligned}
\end{equation}
%
We can solve for the KKT multipliers by noting that
%
\begin{equation*}
  \mu^\nu_{ij} \M^\nu_{ij} = 0,
  \qquad \text{and} \qquad
  \sum_{j: j \neq i} \mu^\nu_{ii} \M^\nu_{ij} 
      = \mu^\nu_{ii} (1 - \M^\nu_{ii}) = \mu^\nu_{ii}.
\end{equation*}
%
Then, with some new vectors defined:
%
\begin{equation}\label{eq:kktsol}
\begin{aligned}
  \mu^\nu_{mm} &= - \eq_m \prn{ r \alb^\nu_m(s) 
    + r \lambda \omb^\nu_i(0) 
    + \prn{r \mathbf{c}_m(s) + (-1)^\nu} \omb^\nu_m(s)
    }, \\
  \mu^\nu_{mn} &= \eq_m \big( 
      r \brk{ \thb_n(s) - \thb_m(s) - \alb^\nu_m(s) }
    + r \lambda \brk{ \etw_n(0) - \etw_m(0) - \omb^\nu_m(0) } 
  \\ &\phantom{= - \eq_m \big( }
    + \brk{rc_m(s) + (-1)^\nu} 
        \brk{ \etw_n(s) - \etw_m(s) - \omb^\nu_m(s) }
     \big), \\
  &\text{where} \quad 
  \boldsymbol{\alpha}^\nu(s) = (\M^\nu - \I) \thb(s), \qquad
  \boldsymbol{\omega}^\nu(s) = (\M^\nu - \I) \etw(s).
\end{aligned}
\end{equation}
%

The expressions in \cref{eq:finitederivs} have the same form as for $s=0$, which allowed us to argue that the model with maximal area must have the serial topology, \cite{Lahiri2013synapse}.

The one missing ingredient is the scale invariance.
Define the scale transformation:
%
\begin{equation}\label{eq:scale}
  \lambda * \M^\nu \equiv (1-\lambda)\I + \lambda \M^\nu.
\end{equation}
%
The Laplace transform has the following scaling property
%
\begin{equation}\label{eq:laplacescale}
  \hat{A} \prn{\lambda s;\lambda * \M^\nu} = \hat{A} \prn{s; \M^\nu}.
\end{equation}
%
At $s=0$, it is scale invariant.
This means that we can take a pair of matrices that violates the ``diagonal'' constraints (second inequality of \eqref{eq:constri}) and use the scale transform \eqref{eq:scale} to construct a pair of matrices that satisfy the ``diagonal'' constraints and have the same area.
This allowed us to ignore the diagonal constraints.
We can't do that for $s>0$.

The corresponding symmetry here is scaling the shifted process from \cref{eq:lshiftpd}, which amounts to
%
\begin{equation}\label{eq:shiftscale}
  \lambda {\circledast}_{s} \M \equiv (1 - \lambda) \I + \lambda \M^\nu
                + \frac{(\lambda - 1) s}{r} (\onev \eq - \I).
\end{equation}
%
Then we have
%
\begin{equation}\label{eq:lshiftscale}
  \hat{A} \prn{s; \M^\nu} 
    = \hat{A} \prn{0, \shift{\M}^\nu(s)}
    = \hat{A} \prn{0, \lambda * \shift{\M}^\nu(s)}
    = \hat{A} \prn{s, \lambda {\circledast}_{s} \M^\nu}.
\end{equation}
%
The problem here is that the lower bound, \(\M^\nu_{ij} \geq 0\), is not invariant under this transformation, unlike the \(s = 0\) case.
Using this transformation to fix the upper bound can break the lower bound.

@@

%-------Section------------------------------------------------------------------

\subsection{Shifted problem}\label{sec:lshift}

The relation of the Laplace transform to the shifted process from \cref{eq:lshiftpd,eq:lareashift} suggests an alternative approach: 
treat the off-diagonal components of \(\shift{\M}^\nu \) as the degrees of freedom and maximise the area instead.
The constraints on \(\shift{\M}^\nu_{ij}\) are different from \cref{eq:constri}:
%
\begin{equation}\label{eq:lshiftconstr}
  \shift{\M}^\nu_{ij} \geq \frac{s \eq_j}{r},
    \quad \forall \; \nu, i, j : i \neq j, \qquad
  \sum_{j: j \neq i} \shift{\M}^\nu_{ij} \leq 1 + \frac{s}{r} (1 - \eq_i).
    \quad \forall \; \nu, i.
\end{equation}
%
The diagonal elements are still given by \( \shift{\M}^\nu_{ii} = 1 - \sum_{j: j \neq i} \shift{\M}^\nu_{ij} \), but now they are allowed to be negative.

The Lagrangian we should consider is
%
\begin{equation}\label{eq:lshiftlagrangian}
\begin{aligned}
  \CL =&\, \sum_{ij} \eq_i \enc_{ij} (\etw_i - \etw_j)
        +\sum_{\nu i j}  f^\nu \mu^\nu_{ij}\prn{\M^\nu_{ij} -  \frac{s}{r} (\eq_j - \delta_{ij}) }
        &+ \lambda \prn{ \Delta\pr - \sum_i \eq_i\w_i },
\end{aligned}
\end{equation}
%
where all of the first-passage times are evaluated at \(s = 0\).
